Molecular Gas \old{Dynamics} \new{Kinematics} of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-11-15 WRITEUP/diff.tex
diff version, doesn't have BH reoil for now

% -------------------------------------- Final Edit Markup ----------------------------------
\usepackage[normalem]{ulem}
\usepackage[usenames]{xcolor}
\definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\newcommand{\new}[1]{\textcolor{red}{\bf #1}}
\newcommand{\old}[1]{\sout{\textcolor{airforceblue}{\bf #1}}} % {\textcolor{green!55!blue}{\bf #1}} or  {\textcolor{OliveGreen}{\bf #1}}
% -----------------------------------------------------------------------------------------------

@@

\citestyle{aa}
\shorttitle{Molecular Gas Kinematics of the Strongly-lensed Quasar Host Galaxy RXJ1131$-$1231}
\shortauthors{Leung, Riechers \& Pavesi}

@@

\title{Molecular Gas Kinematics of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231}
\author{T. K. Daisy Leung, Dominik A. Riechers, and Riccardo Pavesi}
\affil{Department of Astronomy, Space Sciences Building, Cornell University,
Ithaca, NY 14853, USA; \myemail}

@@

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\ssim1.4\E{10}\,\Msun
and \ssim2\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
The gas mass fraction of $\sim$18\% inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
We find lensing-corrected stellar and dust masses, an IR luminosity, and a
star formation rate of
$M_{*}$\ssim3\E{10}\,\Msun, $M_{\rm dust}$\ssim3\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\ssim120\,\sfrU for RXS\,J1131$-$1231.
The source-plane morphologies of its gas and stellar populations
indicate that the star-formation activity may be as extended as the molecular gas reservoir.
We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{0.11}{0.08}\% which is higher
than the 
local value, suggesting that the bulk of the black hole mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.
\end{abstract}

@@

%--------------------------------------------------------------------------
%                          Observations details
%--------------------------------------------------------------------------
\section{Observations} \label{sec:obs}
\subsection{PdBI \bco}
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz) at the tuning frequency of 
$\nu_{\rm obs}$\eq139.256\,GHz
% redshifted to $\nu_{\rm obs}$\eq139.40739\,GHz
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

@@

\subsection{CARMA \cco}
Observations of the \cco rotational line in RXJ1131
($\nu_{\rm rest}$\,=\,345.79599\,GHz) 
% redshifted to 
at the observe frequency of $\nu_{\rm obs}$\eq209.10443\,GHz    % i.e. where we thought the line was redshifted to 
were carried out with the \carma (CARMA;
Program ID: cf0098; PI: D. Riechers)
in the D array configuration on 2014 February 02 under poor 1.5\,mm
weather conditions and on 2014 February 17 under good 1.5\,mm
weather conditions.
This resulted in a total on-source time of 2.94 hours after flagging poor
visibility data.
The correlator setup provides a bandwidth of 3.75 GHz in
each sideband and a %native
spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
(second track) were observed
every 15 minutes for pointing, amplitude, and phase calibration. Mars was
observed as the primary absolute flux calibrator and 3C279 was observed as
the bandpass calibrator for both tracks.

@@

%--------------------------------------------------------------------------
%                                Results
%--------------------------------------------------------------------------
\section{Results} \label{sec:results}
The observed properties of \bco and \cco emission are summarized in \Tab{obsprop}.
\input{table_obsprop}

\subsection{\bco Emission} \label{sec:CO21}
We detect \bco line emission toward the background source in the PdBI data
at $\gtrsim$\,27$\sigma$ significance, enabling us to constrain its redshift at 
$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\footnote{This redshift is derived by fitting a double-Gaussian to 
the de-lensed spectrum, which is shown in \Fig{delensed}.
% instead of the observed spectrum (\Fig{CO21spec}) to avoid biases in our 
% redshift determination of the dynamical center due to differential lensing (see \Sec{differential}).
}. The emission is spatially and kinematically resolved
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 mJy and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
$\Delta v_{\rm sep}$\eq400\pmm12\,\kms. The total integrated line flux is 20.3\,$\pm$\,0.6 Jy \kms. % see 15May16/

\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{Continuum-subtracted spectrum (histogram) of \bco emission towards RXJ1131, with a spectral resolution of
21.5\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
The velocity scale is with respect to $z$\,=\,0.6541, which corresponds to the line center of RXJ1131 based on
the de-lensed line profile (\Fig{delensed}).
A detailed discussion of this effect is presented in \Sec{differential}. \label{fig:CO21spec}}
\end{figure}
\vspace{.2em}
% moment 0 map, highest SNR: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
% - sigma = 0.305 Jy km/s/Beam
%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
We construct a zeroth order moment map, red/blue channel maps, and
first and second moment maps, as shown in \Fig{CO21mom},
using the $uv$-continuum subtracted data cube over a velocity range of
$\Delta v$ $\sim$ 750\,\kms.
The higher-order moment maps are produced using
unbinned channel maps with 3$\sigma$ clipping.
The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
in the intensity map.

The deconvolved source size FWHM from fitting a single two-dimensional Gaussian 
to the integrated line image yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7, 
consistent with the results obtained by $uv$-plane fitting within the uncertainties. 
% UV plane: E_GAUSS: 4.5 +/- 0.1 x 3.5 +/- 0.2
To model the complex spatial distribution of the line emission (\Fig{CO21mom}), we 
fit two independent Gaussians and find deconvolved source sizes of 
3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3.
Therefore, the emission is slightly resolved over $\sim$\,2 beams.
The lensed CO emission is unlikely to be distributed as Gaussians 
given the morphology seen in optical and \nir emission that were observed at higher resolution, 
i.e., the lensed emission of CO (without beam convolution) is more likely to have 
an annulus configuration enclosing a partially complete ``Einstein ring'' with 
structures along the arc 
and knots (see \Fig{CO21mom}). Nevertheless, the deconvolved source sizes and the
spatially offset blue wing compared to optical emission suggest that 
the CO-emitting region in RXJ1131 is more extended than its stellar (and of course quasar) emission.

\begin{figure*}[!htbp]
\hspace{0.5em}
% total chan range = 126-160, which is consistent with mom0 map now (see 15May16)
% 126-144 (Red)
% ~ delta V ~410 km/s
% from [409, 0] km/s
%  144-160 (Blue)
% ~ 365 km/s
% [-324.88, 0] km/s
\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{../Figures/F555WCO21_mom0_single_invertedgray.eps}
\includegraphics[trim=5 -18 0 0, clip, width=0.462\textwidth]{../Figures/F555W_REDBLUE.eps}
\\
\includegraphics[trim=25 16 0 10, clip, width=0.85\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
\vspace{0.1em}
\caption{Top left: overlay of the velocity-integrated \bco emission on an archival {\it HST} $V$-band (F555W)
image.
Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission, which
are extracted by integrating over $v$\,$\in$[$-$19, 357] \kms and $\in$[$-$395, $-$19] \kms, respectively.
The contours in both top panels start at 3$\sigma$ and increment at steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne for the top left panel,
and
$\sigma$ = 0.4 mJy beam\pmOne (red) and 0.5 mJy beam\pmOne (blue)
for the top right panel.
The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295.
Contours for the first (bottom left) and second (bottom right) moment maps of the \bco line emission
are shown in steps of
50 \kms, and 100 \kms, respectively.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$.
\label{fig:CO21mom}}
\end{figure*}

@@

\subsection{\cco Emission}
We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim$\,5$\sigma$ significance.
The spectrum is shown in \Fig{co32spec} and appears to be consistent with a
double-peaked profile. We estimate a line intensity of
35.7\,$\pm$\,6.9\,Jy\,\kms by summing up fluxes over the FWZI
linewidth used to infer the \bco line intensity ($\sim$700 \kms).
Assuming the spatial extent of \bco and \cco is similar and therefore the emission is
magnified by the same amount, the measured line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.78\,$\pm$\,0.62, where this uncertainty includes 
those introduced in absolute flux calibration and is dominated by 
the large phase errors associated with the \cco observations.
This ratio is consistent with
thermalized excitation within the uncertainties, as commonly observed in nuclear regions of
nearby ULIRGs and high-$z$ quasars \citep[e.g.,][]{Weiss07a, CW13}, but also
with the lower excitation seen in normal star-forming disks \citep[e.g.,][]{Dannerbauer09a, CW13}.
% see DANNERBAUER09 intro
% i.e., we cannot rule out the possibility that this guy is similar to gal. pop. of either SF modes.

\begin{figure}[!htbp]
%\centering
\includegraphics[width=0.455\textwidth]{../Figures/coOverlay.eps}
\caption{CARMA \cco line profile (solid) without continuum subtraction is
over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
The velocity scale is with respect to $z$=0.6541, which corresponds to the
line center of \bco line emission. The spectral resolution for \cco and \bco
is 35.8 \kms and 21.5 \kms, respectively.
 \label{fig:co32spec}}
\end{figure}

\subsection{Continuum Emission} \label{sec:deblend}
No 1.4\,mm continuum emission is detected at the position of \cco
down to a 3$\sigma$ limit of 2.49\,mJy beam\pmOne.
This is consistent with the spectrum shown in \Fig{co32spec}.

We detect 2.2\,mm continuum emission at an
 integrated flux density of
1.2\pmm0.2 mJy, with a peak flux of
$S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne
centered on the lensing galaxy (\Fig{cont}).
We note that the reported flux uncertainties do not include those from absolute flux calibration.
Slightly extended emission
along the lensed arc is also detected.
This suggests that we detect emission in both
the foreground galaxy and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in the $uv$-plane to remove the unresolved part of the
emission, which we here assume to be dominated by the foreground galaxy. The peak emission 
of flux $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy
in the residual map coincides with the lensed arc, and is consistent with
the difference between the integrated and the peak flux in the
original continuum map ($\sim$0.4 mJy). 
We therefore adopt $S_{\nu}$\eq0.39\pmm0.22 mJy as the 2\,mm continuum flux measurement for 
the background galaxy (RXJ1131). 
The quoted uncertainty is solely based on the uncertainties associated with the flux density of the 
point source model ($\delta S_{\nu}$\eq0.088\,mJy) and 
that of the integrated flux in the original data (0.2\,mJy), and does not account for that in the 
de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
We report the peak flux in the original map
($S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne) for the foreground galaxy, which
is the best estimate possible at the resolution of our observations, but we acknowledge that a non-negligible contribution from the background source to the peak flux cannot be ruled out.
% The quote uncertainty on the flux density of the foreground galaxy based on the peak flux density
% assumes that the foreground galaxy is a point source, the...

\begin{figure}[!htbp]
%\centering
\includegraphics[trim=12 27 0 1, clip, width=0.475\textwidth]{../Figures/F555W_ContPdBI.eps}
\includegraphics[trim=10 5 0 0, clip, width=0.4695\textwidth]{../Figures/F555W_ContVLA.eps}
\caption{Top: overlay of the 2\,mm continuum emission on the optical image.
Contours start and increment at steps of
$\pm$3$\sigma$, where $\sigma_{\rm 2mm}$\,=\,0.082 mJy beam\pmOne.
Bottom: overlap of the VLA 5\,GHz continuum emission on the optical image.
Contours correspond to [10, 40, 60, 100]\%$\times$ the peak flux density of $S_{\rm 5GHz}$\eq0.74\pmm0.01 mJy.
% Radio emission towards the foreground radio core is detected at $\gtrsim$57$\sigma$,
% where $\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne.
The central crosses in both panels indicate the centroid of the foreground galaxy,
as detected in the optical image. 
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$ for
the PdBI observations (top), and
0\farcs5 $\times$ 0\farcs4 (PA = 0.18$\degr$) for
the VLA observations (bottom).
\label{fig:cont}}\vspace{0.51em}
\end{figure}

>>>>

% -------------------------------------- Final Edit Markup ----------------------------------
\usepackage[normalem]{ulem}
\usepackage{soul}
\usepackage[usenames]{xcolor}
\definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\newcommand{\new}[1]{\textcolor{red}{\bf #1}}
\newcommand{\old}[1]{\textcolor{airforceblue}{\protect\st{#1}}} % {\textcolor{green!55!blue}{\bf #1}} or  {\textcolor{OliveGreen}{\bf #1}}
% -----------------------------------------------------------------------------------------------

@@

\citestyle{aa}
\shorttitle{Molecular Gas \old{Dynamics} \new{Kinematics} of the Strongly-lensed Quasar Host Galaxy RXJ1131$-$1231}
\shortauthors{Leung, Riechers \& Pavesi}

@@

\title{Molecular Gas \old{Dynamics} \new{Kinematics} of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231}
\author{T. K. Daisy Leung, Dominik A. Riechers, and Riccardo Pavesi}
\affil{Department of Astronomy, Space Sciences Building, Cornell University,
Ithaca, NY 14853, USA; \myemail}

@@

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\ssim1.4\E{10}\,\Msun
and \ssim2\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
The gas mass fraction of \old{$\sim$19\% } \new{$\sim$18\%} inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
We find lensing-corrected stellar and dust masses, an IR luminosity, and a
star formation rate of
$M_{*}$\ssim3\E{10}\,\Msun, $M_{\rm dust}$\ssim\old{4}\new{3}\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\ssim120\,\sfrU for RXS\,J1131$-$1231.
The source-plane morphologies of its gas and stellar populations
indicate that the star-formation activity may be as extended as the molecular gas reservoir.
We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of \old{\protect$>$0.27\petm{11}{8}\%} \new{$>$0.27\petm{0.11}{0.08}\%} which is higher
than the 
local value, suggesting that the bulk of the black hole mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.
\end{abstract}

@@

%--------------------------------------------------------------------------
%                          Observations details
%--------------------------------------------------------------------------
\section{Observations} \label{sec:obs}
\subsection{PdBI \bco}
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz) 
\old{at the $\nu_{\rm LO}$\eq139.256\,GHz}
\new{at the tuning frequency of $\nu_{\rm obs}$\eq139.256\,GHz}
% redshifted to $\nu_{\rm obs}$\eq139.40739\,GHz
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

@@

\subsection{CARMA \cco}
Observations of the \cco rotational line in RXJ1131 \old{($\nu_{\rm rest}$\,=\,345.79599\,GHz) redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz}
\new{($\nu_{\rm rest}$\,=\,345.79599\,GHz) 
% redshifted to 
at the observe frequency of $\nu_{\rm obs}$\eq209.10443\,GHz}    % i.e. where we thought the line was redshifted to 
were carried out with the \carma (CARMA;
Program ID: cf0098; PI: D. Riechers)
in the D array configuration on 2014 February 02 under poor 1.5\,mm
weather conditions and on 2014 February 17 under good 1.5\,mm
weather conditions.
This resulted in a total on-source time of 2.94 hours after flagging poor
visibility data.
The correlator setup provides a bandwidth of 3.75 GHz in
each sideband and a %native
spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
(second track) were observed
every 15 minutes for pointing, amplitude, and phase calibration. Mars was
observed as the primary absolute flux calibrator and 3C279 was observed as
the bandpass calibrator for both tracks.

@@

%--------------------------------------------------------------------------
%                                Results
%--------------------------------------------------------------------------
\section{Results} \label{sec:results}
\new{The observed properties of \bco and \cco emission are summarized in \Tab{obsprop}.
\input{table_obsprop}}

\subsection{\bco Emission} \label{sec:CO21}
We detect \bco line emission toward the background source in the PdBI data
at $\gtrsim$\,27$\sigma$ significance, \old{confirming the redshift at $z_{\rm CO}$\eq0.6537\,$\pm$\,0.0005.} \new{enabling us to constrain its redshift at 
$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\footnote{This redshift is derived by fitting a double-Gaussian to 
the de-lensed spectrum, which is shown in \Fig{delensed}.
% instead of the observed spectrum (\Fig{CO21spec}) to avoid biases in our 
% redshift determination of the dynamical center due to differential lensing (see \Sec{differential}).
}}. \old{The emission is spatially and dynamically resolved} \new{The emission is spatially and kinematically resolved}
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 mJy and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
$\Delta v_{\rm sep}$\eq400\pmm12\,\kms. The total integrated line flux is \old{24.1\,$\pm$\,2.3 Jy \kms} \new{20.3\,$\pm$\,0.6 Jy \kms}. % see 15May16/

\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{Continuum-subtracted spectrum (histogram) of \bco emission towards RXJ1131, with a spectral resolution of
21.5\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
The velocity scale is with respect to \old{$z$\,=\,0.6537, which is approximately the line center considering the asymmetry resulting from differential lensing.} \new{$z$\,=\,0.6541, which corresponds to the line center of RXJ1131 based on
the de-lensed line profile (\Fig{delensed})}.
A detailed discussion of this effect is presented in \Sec{differential}. \label{fig:CO21spec}}
\end{figure}
\vspace{.2em}
% moment 0 map, highest SNR: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
% - sigma = 0.305 Jy km/s/Beam
%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
We construct a zeroth order moment map, red/blue channel maps, and
first and second moment maps, as shown in \Fig{CO21mom},
using the $uv$-continuum subtracted data cube over a velocity range of
$\Delta v$ $\sim$ 750\,\kms.
The higher-order moment maps are produced using
unbinned channel maps with 3$\sigma$ clipping.
The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
in the intensity map.

\old{\protect{
The deconvolved source size FWHM obtained by fitting a two-dimensional Gaussian to the integrated line map in
the image plane
is 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
and thus, the emission is resolved over $\sim$2.2 beams.
While the lensed emission is not strictly distributed as a two-dimensional
Gaussian;
the fit recovers the line intensity enclosed by the emitting
region, therefore we take this as an estimate on the full extent of the lensed
emission. On the other hand, if we assume that the spatial distribution of
the lensed molecular gas emission is similar to that in the optical to \nir
wavelengths, the lensed emission would be more accurately described by an
annulus, enclosing the partially complete ``Einstein ring'' and
the lensed knots (see \Fig{CO21mom}).}}
\new{The deconvolved source size FWHM from fitting a single two-dimensional Gaussian 
to the integrated line image yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7, 
consistent with the results obtained by $uv$-plane fitting within the uncertainties. 
% UV plane: E_GAUSS: 4.5 +/- 0.1 x 3.5 +/- 0.2
To model the complex spatial distribution of the line emission (\Fig{CO21mom}), we 
fit two independent Gaussians and find deconvolved source sizes of 
3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3.
Therefore, the emission is slightly resolved over $\sim$\,2 beams.
The lensed CO emission is unlikely to be distributed as Gaussians 
given the morphology seen in optical and \nir emission that were observed at higher resolution, 
i.e., the lensed emission of CO (without beam convolution) is more likely to have 
an annulus configuration enclosing a partially complete ``Einstein ring'' with 
structures along the arc 
and knots (see \Fig{CO21mom}). Nevertheless, the deconvolved source sizes and the
spatially offset blue wing compared to optical emission suggest that 
the CO-emitting region in RXJ1131 is more extended than its stellar (and of course quasar) emission.}

\begin{figure*}[!htbp]
\hspace{0.5em}
% total chan range = 126-160, which is consistent with mom0 map now (see 15May16)
% 126-144 (Red)
% ~ delta V ~410 km/s
% from [409, 0] km/s
%  144-160 (Blue)
% ~ 365 km/s
% [-324.88, 0] km/s
\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{../Figures/F555WCO21_mom0_single_invertedgray.eps}
\includegraphics[trim=5 -18 0 0, clip, width=0.462\textwidth]{../Figures/F555W_REDBLUE.eps}
\\
\includegraphics[trim=25 16 0 10, clip, width=0.85\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
\vspace{0.1em}
\caption{Top left: overlay of the velocity-integrated \bco emission on an archival {\it HST} $V$-band (F555W)
image.
Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission, which
\old{\protect{are extracted by integrating over $v$\,$\in$[0, 409] \kms and $\in$[$-$325,0] \kms, respectively.}}
\new{\protect{are extracted by integrating over $v$\,$\in$[$-$19, 357] \kms and $\in$[$-$395, $-$19] \kms, respectively.}}
The contours in both top panels start at 3$\sigma$ and increment at steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne for the top left panel,
and
$\sigma$ = 0.4 mJy beam\pmOne (red) and 0.5 mJy beam\pmOne (blue)
for the top right panel.
The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295.
Contours for the first (bottom left) and second (bottom right) moment maps of the \bco line emission
are shown in steps of
50 \kms, and 100 \kms, respectively.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$.
\label{fig:CO21mom}}
\end{figure*}

@@

\subsection{\cco Emission}
We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim$\,5$\sigma$ significance.
The spectrum is shown in \Fig{co32spec} and appears to be consistent with a
double-peaked profile. We estimate a line intensity of
\old{35.7\,$\pm$\,21.9 Jy\,\kms} \new{35.7\,$\pm$\,6.9\,Jy\,\kms} by summing up fluxes over the FWZI
linewidth used to infer the \bco line intensity ($\sim$700 \kms).
Assuming the spatial extent of \bco and \cco is similar and therefore the emission is
magnified by the same amount, the measured line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,\old{0.66\,$\pm$\,0.41. Taking into account the large phase errors associated with \cco, this is consistent with}
\new{0.78\,$\pm$\,0.62, where this uncertainty includes 
those introduced in absolute flux calibration and is dominated by 
the large phase errors associated with the \cco observations.
This ratio is consistent with}
thermalized excitation within the uncertainties, as commonly observed in nuclear regions of
nearby ULIRGs and high-$z$ quasars \citep[e.g.,][]{Weiss07a, CW13}, but also
with the lower excitation seen in normal star-forming disks \citep[e.g.,][]{Dannerbauer09a, CW13}.
% see DANNERBAUER09 intro
% i.e., we cannot rule out the possibility that this guy is similar to gal. pop. of either SF modes.

\begin{figure}[!htbp]
%\centering
\includegraphics[width=0.455\textwidth]{../Figures/coOverlay.eps}
\caption{CARMA \cco line profile (solid) without continuum subtraction is
over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
The velocity scale is with respect to \old{\protect{$z$=0.6537, which corresponds to the
dynamical center of the \bco line.}} \new{\protect{$z$=0.6541, which corresponds to the
line center of \bco line emission.}} The spectral resolution for \cco and \bco
is 35.8 \kms and 21.5 \kms, respectively.
 \label{fig:co32spec}}
\end{figure}

\subsection{Continuum Emission} \label{sec:deblend}
No \old{1.5\,mm} \new{1.4\,mm} continuum emission is detected at the position of \cco
down to a 3$\sigma$ limit of 2.49\,mJy beam\pmOne.
This is consistent with the spectrum shown in \Fig{co32spec}.

We detect \old{2\,mm} \new{2.2\,mm} continuum emission at an
 integrated flux density of
1.2\pmm0.2 mJy, with a peak flux of
$S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne
centered on the lensing galaxy (\Fig{cont}).
\new{We note that the reported flux uncertainties do not include those from absolute flux calibration.}
Slightly extended emission
along the lensed arc is also detected.
This suggests that we detect emission in both
the foreground galaxy and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in the $uv$-plane to remove the unresolved part of the
emission, which we here assume to be dominated by the foreground galaxy. The peak emission 
\old{(0.39\,$\pm$\,0.08\,mJy)}
\new{of flux $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy}
in the residual map coincides with the lensed arc, and is consistent with
the difference between the integrated and the peak flux in the
original continuum map ($\sim$0.4 mJy). 
We therefore adopt \old{$S_{\nu}$ = 0.39\pmm0.08 mJy} \new{$S_{\nu}$\eq0.39\pmm0.22 mJy} as the 2\,mm continuum flux measurement for 
the background galaxy (RXJ1131). 
\old{The quoted uncertainty is from the flux measurement in the residual map, }
\new{The quoted uncertainty is solely based on the uncertainties associated with the flux density of the 
point source model ($\delta S_{\nu}$\eq0.088\,mJy) and 
that of the integrated flux in the original data (0.2\,mJy), }and does not account for that in the 
de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
We report the peak flux in the original map
($S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne) for the foreground galaxy, which
is the best estimate possible at the resolution of our observations, but we acknowledge that a non-negligible contribution from the background source to the peak flux cannot be ruled out.
% The quote uncertainty on the flux density of the foreground galaxy based on the peak flux density
% assumes that the foreground galaxy is a point source, the...

\begin{figure}[!htbp]
%\centering
\includegraphics[trim=12 27 0 1, clip, width=0.475\textwidth]{../Figures/F555W_ContPdBI.eps}
\includegraphics[trim=10 5 0 0, clip, width=0.4695\textwidth]{../Figures/F555W_ContVLA.eps}
\caption{Top: overlay of the 2\,mm continuum emission on the optical image.
Contours start and increment at steps of
$\pm$3$\sigma$, where $\sigma_{\rm 2mm}$\,=\,0.082 mJy beam\pmOne.
Bottom: overlap of the VLA 5\,GHz continuum emission on the optical image.
\new{Contours correspond to [10, 40, 60, 100]\%$\times$ the peak flux density of $S_{\rm 5GHz}$\eq0.74\pmm0.01 mJy.}
% Radio emission towards the foreground radio core is detected at $\gtrsim$57$\sigma$,
% where $\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne.
The central crosses in both panels indicate the centroid of the foreground galaxy,
as detected in the optical image. 
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$ for
the PdBI observations (top), and
0\farcs5 $\times$ 0\farcs4 (PA = 0.18$\degr$) for
the VLA observations (bottom).
\label{fig:cont}}\vspace{0.51em}
\end{figure}
